Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-21 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Answer a question in the draft

```{r}
rain_exposure$county_storm <- transmute(rain_exposure, county_storm = paste0(fips, " ", storm_id))
distance_exposure$county_storm <- transmute(distance_exposure, county_storm = paste0(fips, " ", storm_id))
all_exposure <- full_join(rain_exposure, distance_exposure, by = "county_storm")
both_exposure <- subset(all_exposure, tot_precip >= 75 & storm_dist.x <= 100) #4040 observations
rain_only <- subset(all_exposure, tot_precip >= 75 & storm_dist.x > 100) #4200 obs
distance_only <- subset(all_exposure, tot_precip < 75 & storm_dist.x <= 100) #0 obs
sum(all_exposure$tot_precip >= 75 & all_exposure$storm_dist.x <= 100, na.rm = TRUE)
sum(all_exposure$tot_precip >= 75 & all_exposure$storm_dist.x > 100, na.rm = TRUE)
sum(all_exposure$tot_precip < 75 & all_exposure$storm_dist.x <= 100, na.rm = TRUE) # It appears that in all county-
                                                                                   # storm pairs, there is ample
                                                                                   # rain to meet criteria        
sum(all_exposure$tot_precip < 75, na.rm = TRUE) # This also returns 0
```

JMF-- I was surprised to see that there were no observations in the data frame that had total precipitation less than 75 mm. I am wondering if I am missing something in the `full_join` code

>>>>

```{r}
rain_exposure$county_storm <- transmute(rain_exposure,
                                        county_storm = paste0(fips, " ",
                                                              storm_id))
distance_exposure$county_storm <- transmute(distance_exposure,
                                            county_storm = paste0(fips, " ",
                                                                  storm_id))
all_exposure <- rain_exposure %>% 
        dplyr::select(county_storm, tot_precip) %>%
        dplyr::full_join(distance_exposure, by = "county_storm")  %>%
        dplyr::mutate(rain_exposure =  !is.na(tot_precip) & 
                              tot_precip >= 75,
                      dist_exposure = !is.na(storm_dist) & 
                              storm_dist < 100,
                      both_exposures = rain_exposure & dist_exposure,
                      rain_only = rain_exposure & !dist_exposure,
                      dist_only = !rain_exposure & dist_exposure,
                      neither_exposure = !rain_exposure & !dist_exposure) %>%
        dplyr::summarize(both_exposure = sum(both_exposures),
                         rain_only = sum(rain_only),
                         dist_only = sum(dist_only),
                         neither_exposure = sum(neither_exposure))
all_exposure

# both_exposure <- subset(all_exposure, tot_precip >= 75 & 
#                                 storm_dist <= 100) #4040 observations
# rain_only <- subset(all_exposure, tot_precip >= 75 & 
#                             storm_dist.x > 100) #4200 obs
# distance_only <- subset(all_exposure, tot_precip < 75 & 
#                                 storm_dist.x <= 100) #0 obs
# sum(all_exposure$tot_precip >= 75 & all_exposure$storm_dist.x <= 100,
#     na.rm = TRUE)
# sum(all_exposure$tot_precip >= 75 & all_exposure$storm_dist.x > 100,
#     na.rm = TRUE)
# sum(all_exposure$tot_precip < 75 & all_exposure$storm_dist.x <= 100,
#     na.rm = TRUE) # It appears that in all county-
#                                                                                    # storm pairs, there is ample
#                                                                                    # rain to meet criteria        
# sum(all_exposure$tot_precip < 75, na.rm = TRUE) # This also returns 0
```

JMF-- I was surprised to see that there were no observations in the data frame that had total precipitation less than 75 mm. I am wondering if I am missing something in the `full_join` code. [GBA-- I've re-done this code and it now looks like it's getting the same values as your code below.]
